---
title: "week 03 coding challenge"
author: "Stephen Omotayo Ololade."
date: ""08/02/2022
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
```


```{r load libraries}

```

# load dataset
```{r load data}
data.01 <-read_csv("Data/LHS_exercise_02042022.csv") 

```

We want to explore whether higher risk of depression increases alcohol consumtion. 

Based on the Latino Health Survey codebook, the four items of depression (PTSD-4; page 6) need to be reversed.

Your task is to manipulate your data using the `tidyverse`'s `mutate`, `case_when` functions and run a series of logistic regression analyses. Use Google search as needed.

Challenge 1: mutate new variables: 
- `ptsd_mean` (average of four ptsd items)
- `ptsd_mean_rev` (reverse of the `ptsd_mean` variable; hint: 6- value)
- `ptsd_mean_rev_std` (standardized value of `ptsd_mean`)
- `audit_c` (participants who responded 1 or 2 ~ 1; else ~0)

```{r}
data02 <-data01%>%
  mutate(ptsd_mean =rowMeans (across(ptsd1_1:ptsd4_1),
                              na.rm = TRUE),
         ptsd_mean_rev =6-ptsd_mean,
         ptsd_mean_rev_std = scale(ptsd_mean_rev),
         audit_c = case_when(audit1 <= 2~  1,
                             TRUE ~0))

         


```


For your reference: (pg 8 of the codebook)
How often did you have a drink containing alcohol in the past year? 
1. Four or more times a week <-- coded as '1' 
2. Two to three times per week <-- coded as '1'
3. Two to four times a month <-- coded as '0'
4. Monthly or less <- coded as '0'
5. Never <- coded as '0'

   # data wrangling
```{r}
data03 <- data02%>%
  select(age,education,sex,ptsd_mean, ptsd_mean_rev, ptsd_mean_rev_std,audit_c)

data04 <- data03%>% 
  select(age,education,sex, ptsd_mean_rev, ptsd_mean_rev_std,audit_c)

```



#Now we will be running several logistic regression and compare the results:

Run logistic regression using `ptsd_mean_rev` adjusting for age, sex, and education; use `tidy` function for output; exponent your results and interpret your result using odds ratio
```{r logistic regression 1

```{r}

data05 <- data04%>%
  mutate(ptsd_mean_rev_bi =case_when(ptsd_mean_rev >=7 ~1,
                                     TRUE ~0))
ftable(data05$ptsd_mean_rev_bi)

          

```

#let's fit logistic regression
```{r}

fit.1 <- glm (ptsd_mean_rev_bi ~ age+ factor(sex)+ factor(education),
             family = binomial (link ="logit"),
             data=data05) 
  

summary(fit.1)   

#let's exponentiate

coef(fit.1)

exp(coef(fit.1))
    
  
```
#using tidy 
```{r}

tidy(fit.1, conf.int = T, exponentiate = TRUE)

```






```

Interpretation: 
# all the respondents fall into depression risk
## 

```{r}
# all the respondents fall into depression risk
## 
```


Use `ggfortify`'s `autoplot` function to do model diagnostics
```
```{r}
autoplot(fit.1, 
         which = 1:6,
         ncol =2)

```


```

Explain diagnostic plots:
[It contains only numeric valus ]



Run logistic regression using `ptsd_mean_rev_std` adjusting for age, sex, and education; use `tidy` function for output; use `divide-by-four` approach and interpret your result using probability scale. 
```{r}


  
  
  
```
Interpretation
[ ]



#Next, visualization
Use `ggplot` to duplicate the figure
Using the `ptsd_mean_rev` variable you created before, you would need to categorize the mean value into four categories: 
if ptsd_mean_rev is :
1-1.9 ~ 1 ; 
2-2.9 ~2; 
3-3.9 ~ 3; 
4+ ~ 4. 

Refer to Healy's book or Google search as a guide. 

```{r visualization}

```

